NSNEQ_Moon_Example

### 2017-10-18 NSNEQ_Moon_Example.Rmd
My last edits to Moon example before Daniel's comments. Remoced details of original as it was unnecessary for the example.

Shih, Pittinsky, and Ambady (1999) conducted a study to investigate whether Asian-American women would perform better on a maths test when primed with their Asian identity. They found a 5% increase in correct answers compared to an un-primed control group of Asian-American women, d = 0.26, Student t(30) = 0.76, p = 0.45, two-sided). A replication by Moon & Roeder (2014) observed a slightly reversed difference between the Asian primed group (N = 53, M = 0.46, SD = 0.17) and the control (N = 48, M = 0.50, SD - 0.18) which was not significant, d = -0.23, Welch t(96.62) = 1.15, p = 0.26, two-sided). Having failed to obtain a significant result, we are left with two alternatives:

@@

Using the TOSTER package in R, we can then calculate the TOST by insterting the summary statistics from Moon & Roeder (2014), assuming an aplha of 0.05, and using +/- the value of `sesoi.d` (`r sesoi.d`) as our equivalence bounds. We find that the TOST is non-significant, t(96.62) = 0.72, p = 0.24. Thus, we cannot reject the possibility that the true effect really is larger than our SESOI.

>>>>

Moon & Roeder (2014), replicating Shih, Pittinsky, and Ambady (1999), conducted a study to investigate whether Asian-American women would perform better on a maths test when primed with their Asian identity. They observed a slightly reversed difference between the Asian primed group (N = 53, M = 0.46, SD = 0.17) and the control (N = 48, M = 0.50, SD - 0.18) which was not significant, d = -0.23, Welch t(96.62) = 1.15, p = 0.26, two-sided). Having failed to obtain a significant result, we are left with two alternatives:

@@

Using the TOSTtwo function in the TOSTER package in R, we can then calculate the TOST by insterting the summary statistics from Moon & Roeder (2014), assuming an aplha of 0.05, and using +/- the value of `sesoi.d` (`r sesoi.d`) as our equivalence bounds. We find that the TOST is non-significant, t(96.62) = 0.72, p = 0.24. Thus, we cannot reject the possibility that the true effect really is larger than our SESOI.
